LogChunks: A Data Set for Build Log Analysis

### 2020-02-14 msr-paper/paper.tex
Make link clickable

Thus, in this paper, we present
\logchunks~\cite{brandt_carolin_2020_3632351},\footnote{\logchunks is
  openly available on Zenodo: https://zenodo.org/record/3632351} a
collection of 797 labeled Travis CI build logs from 80 highly popular GitHub
repositories in 29 programming languages with  we
manually labeled the chunk describing why the build failed.  The data
set also provides keywords the authors would use to search for the
labeled log chunk and categorizes the log chunks according to their
format within the log.

>>>>

Thus, in this paper, we present
\logchunks~\cite{brandt_carolin_2020_3632351},\footnote{\logchunks is
  openly available on Zenodo: \url{https://zenodo.org/record/3632351}} a
collection of 797 labeled Travis CI build logs from 80 highly popular GitHub
repositories in 29 programming languages with  we
manually labeled the chunk describing why the build failed.  The data
set also provides keywords the authors would use to search for the
labeled log chunk and categorizes the log chunks according to their
format within the log.
